Prefetching SPARQL query cacher

### 2016-05-18 dissertation/cache-proxy.tex
more analysers
more on analysis

\subsection{Linked Data Fragment client}

@@

@@

\begin{itemize}
\item An analyser, used to determine whether certain triple patterns
  should have their results prefetched and cached.
\item A prefetcher that performs the needed actions.
\item Two query planners, one that can use a local cache and a remote
  endpoint, and another that extends this to be able to use Triple
  Pattern Fragments as well, and corresponding models.
\item Two roles to generate plans for accessing cache and Triple
  Pattern Fragments and a corresponding plan class to enter results
  in the cache.
\item A custom User Agent for caching.
\item The actual caching proxy that accepts queries, runs the planner
  and returns the results.
\item Scripts to run the whole system.
\end{itemize}

>>>>

\subsection{Linked Data Fragment client}\label{sec:ldfclient}

@@

It also supplies a plan class \pmodule{AtteanX::Plan::LDF::Triple}
used in the query planning.

@@

\begin{itemize}
\item Analysers, used to determine whether certain triple patterns
  should have their results prefetched and cached.
\item A prefetcher that performs the needed actions.
\item Two query planners, one that can use a local cache and a remote
  endpoint, and another that extends this to be able to use Triple
  Pattern Fragments as well, and corresponding models.
\item Two roles to generate plans for accessing cache and Triple
  Pattern Fragments and a corresponding plan class to enter results
  in the cache.
\item A custom User Agent for caching.
\item The actual caching proxy that accepts queries, runs the planner
  and returns the results.
\item Scripts to run the whole system.
\end{itemize}

\subsubsection{Analysis and prefetching}

Analysers and prefetchers run asynchronously with query
evaluation. This is achieved by an addition to the proxy that sends a
query to a persistent analyser script that subscribes to a channel on
a Redis\footnote{See \url{http://redis.io/}} data structure store.

The analyser script can be configured to use any number of analysers.
Two such analysers have been implemented, for now constrained to
single triple patterns. One will count the predicates in consecutive
queries it sees, and publish triple patterns to another Redis channel
with the predicate if the count exceeds a certain configurable
limit. This is an attempt to capture and cache popular parts of
queries.

The second analyser will rerun the query planner on the incoming query
while simulating that the results of a certain triple pattern was in
the cache. If the cost reduction of the best plan is larger than a
configurable limit, it will publish that triple pattern to the same
Redis channel as above.

Another persistent script is subscribed to this latter channel. If the
Model supports Linked Data Fragments, a retriever will then download
the results of the triple pattern and enter it into the cache, or use
a single triple pattern SPARQL query if not.

The cache itself is assumed to only cache triples where at least one
term is bound. I have used the Redis data structure store for the
cache as well. This choice is somewhat arbitrary, and has not proved
very successful. The cache will store the results as an array if two
RDF terms were bound in the triple pattern, or a hash if only one term
was bound. The strings put into the cache are serialized N-Triples
strings.

In addition to caching the prefetched results, the proxy may also
cache the serialized results of any full SPARQL query, and also enter
the results of any Linked Data Fragment retrieved when the query
planner evaluates a query into the above cache, using a trivial
extension to the plan class in Section~\ref{sec:ldfclient}.

\subsubsection{Query planner}
